Universal Anonymous Signatures

### 2022-10-01 prism-backend/research/gsac/app-building-blocks.tex
Refined model for RAC. Conclusion. Complete draft (excl. app. D)
Added back issuance unforgeability to fix issuance flaw. Updated rest of the paper. Proofs can be improved.

\subsection{Digital Signatures}
\label{sapp:digital-signatures}

@@

\begin{figure}[ht!]
  \begin{minipage}[t]{\textwidth}
    \centering
    \procedure{$\ExpEUF(\Ssecpar)$}{%
      \Sparm \gets \SSetup(\Ssecpar) \\
      (\Svk,\Ssk) \gets \SKeyGen(\Sparm) \\
      (\Ssig,\msg) \gets \adv^{\SSign(\Ssk,\cdot)}(\Svk) \\
      \pcif \SVerify(\Svk,\Ssig,\msg) = 0: \pcreturn 0 \\
      \pcif \msg~\textrm{was not queried to \SSign}: \pcreturn 1 \\
      \pcreturn 0
    }
  \end{minipage}
  \label{fig:euf-game}
  \caption{Existential Unforgeability Game.}
\end{figure}

@@

A commitment scheme is defined by the following algorithms:

@@

To the best of our knowledge, models of existing schemes for signing blocks of
messages like \cite{cl02,asm06,ps16,cdl16b} target the case of signing blocks
of \emph{plain} messages, and are subsequently informally extended to support
signing commitments to blocks of messages via interactive protocols. However,
they do not support signing both committed and plain messages (although the
extension is trivial); and, more importantly, do not give security models of
the resulting construction, nor of course prove its security. While the
extension seems straightforward, the modelling needs to be changed due to the
mentioned nuance of the conventional EUF notion not being compatible with
interactive signing protocols where the signer does not learn (some of) the
signed message(s). As we aim at using this variant as a generic building block,
we briefly model such a scheme for Signatures over Blocks of Committed Messages
(\SBCM).

@@

\begin{description}
\item[$\SBCMparm \gets \SBCMSetup(\SBCMsecpar)$.] It produces public parameters
  for the other algorithms, given an input security parameter \SBCMsecpar.
\item[$(\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm)$.] Generates a
  verification-signing key pair.
\item[$\SBCMsig/\bot \gets \langle \SBCMCom(\SBCMvk,\overline{\smsg},\smsg),
  \SBCMSign(\SBCMsk,\smsg) \rangle$.] An interactive protocol between two
  parties with shared input a block of messages \smsg. The party running
  \SBCMCom further knows a set of messages $\overline{\smsg}$ to be
  block-committed and then signed along with \smsg. The party running \SBCMSign
  controls the signing key \SBCMsk. As a result, both parties get signature
  \SBCMsig over $\smsg \cup \overline{\smsg}$.
\item[$1/0 \gets \SBCMVerify(\SBCMvk,\SBCMsig,\overline{\smsg},\smsg)$.] Checks
  whether \SBCMsig is a valid signature over the set of messages
  $\overline{\smsg}$ and \smsg, under verification key \SBCMvk.
\end{description}

Note that these functionality is just a generalization of partially blind
signature schemes, where both user and signer can produce signatures over
blocks of (committed) messages. The correctness and security properties are
then defined as follows.

\paragraph{Correctness.} %
Informally, an \SBCM scheme is correct if signatures generated between an honest
party running \SBCMCom with message sets $\overline{\smsg}$ and \smsg, and an
honest signer running \SBCMSign over \smsg, for honestly generated parameters
and key pairs, results in a signature over $\overline{\smsg}$ and \smsg that is
accepted by \SBCMVerify.

@@

\paragraph{Blindness.} %
Finally, the signer must not learn the plaintext values of the messages that are
signed in committed form. Note that this is a weaker notion than the usual
blindness property of blind signature schemes, where it is required that the
adversary cannot link a signature to the signing process that produced it.
Formally, blindness for \SBCM schemes is defined as in \ExpSBCMBlindb in
\figref{fig:sbcm-games}. An \SBCM scheme is blind if, for all p.p.t.
adversaries $\adv$, $|\Pr[\ExpSBCMBlindo(\SBCMsecpar) = 1] -
\Pr[\ExpSBCMBlindz(\SBCMsecpar) = 1]|$ is a negligible function of the security
parameter.

\begin{figure}[ht!]
  \begin{minipage}[t]{\textwidth}
    \centering

    \procedure[linenumbering]{$\ExpSBCMOMF(\SBCMsecpar)$}{%
      \SBCMparm \gets \SBCMSetup(\SBCMsecpar) \\
      (\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm) \\
      ((\sig_1,\overline{\smsg}_1, \smsg_1),\dots,
      (\sig_{n+1},\overline{\smsg}_{n+1},\smsg_{n+1})) \gets
      \adv^{\langle \cdot, \SBCMSign(\SBCMsk,\cdot) \rangle}(\SBCMvk) \\
      \pcif \exists i \in [n+1]~\st~\SBCMVerify(\SBCMvk,\sig_i,
      \overline{\smsg}_i,\smsg_i) = 0: \pcreturn 0 \\
      \pcif \exists i \neq j \in [n+1]~\st~\smsg_i = \smsg_j \land
      \overline{\smsg}_i = \overline{\smsg}_j: \pcreturn 0 \\
      \pcif \langle \cdot, \SBCMSign(\SBCMsk,\cdot)\rangle~
      \textrm{was called more than $n$ times}: \pcreturn 0 \\
      \pcreturn 1
    }

    \vspace*{0.5em}

    \procedure[linenumbering]{$\ExpSBCMBlindb(\SBCMsecpar)$}{%
      \SBCMparm \gets \SBCMSetup(\SBCMsecpar) \\
      (\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm) \\
      (\overline{\smsg}_0,\overline{\smsg}_1,\smsg) \gets
      \adv^{\langle \cdot, \SBCMSign(\SBCMsk,\cdot) \rangle}(\SBCMvk) \\
      \csig \gets \langle \SBCMCom(\SBCMvk,\overline{\smsg}_b,\smsg),
      \SBCMSign(\SBCMsk,\smsg) \rangle \\
      b^* \gets \adv^{\langle \cdot, \SBCMSign(\SBCMsk,\cdot) \rangle}(\SBCMvk,
      \csig) \\
      \pcif b = b^*: \pcreturn 1 \\
      \pcreturn 0
    }
  \end{minipage}
  \label{fig:sbcm-games}
  \caption{Games for \SBCM schemes.}
\end{figure}

\paragraph{Augmenting with NIZKs.} %
\todo{This is quite informal. Perhaps expand...} 
In the previous \SBCM scheme, it is straightforward to require that the party
running \SBCMCom proves some arbitrary claim over the messages to be signed
(both those in committed or plaintext form), as well as over possibly extra
auxiliary data. This can be done by having this party add a NIZK over the
corresponding NP statement, which has later to be verified by the party running
\SBCMSign.
%
We use this extension in our \CUASGen construction, and thus extend the previous
syntax for interactive signing  as follows, to account for an extra NIZK
relation \NIZKRel proving that a pair of statement $x$ and witness $w$ belong
\NIZKRel.

\begin{description}
\item[$\SBCMsig/\bot \gets \langle \SBCMCom^{\NIZKRel}(\SBCMvk,\overline{\smsg},
  \smsg,(x,w)),\SBCMSign^{\NIZKRel}(\SBCMsk,\smsg,x) \rangle$.] As before, but
  the party running \SBCMCom, who owns witness $w$ for $x$ in \NIZKRel, proves
  in zero-knowledge to the party running \SBCMSign that $(x,w) \in \NIZKRel$.
\end{description}

Finally, in addition, we require that the produced signatures must be compatible
with (efficient) NIZK proofs of knowledge of a signature, and of (arbitrary)
claims over the signed (committed) messages.

@@

\paragraph{$\SBCMsig/\bot \gets \langle \SBCMCom(\SBCMvk,\overline{\smsg},
  \smsg), \SBCMSign(\SBCMsk,\smsg) \rangle$.} %

\begin{itemize}
\item \underline{User}: If $|\smsg|>\nattrs$ or $|\overline{\smsg}|>\tnattrs$,
  abort. Else, fetch fresh randomness $r \getr \ZZ^*_p$, compute $\Ccom \gets
  \gen{g}^r\prod_{i \in [|\overline{\smsg}|]}\gen{\th}_i^{\overline{\smsg}_i}$,
  and $\NIZKproof \gets \NIZKProve(\NIZKcrs,(r,\overline{\smsg}),\Ccom)$.
  Send $(\Ccom,\NIZKproof)$ to Issuer.
\item \underline{Signer}: If $|\smsg|>\nattrs$, abort. Else, run $\NIZKVerify
  (\NIZKcrs,\Ccom,\NIZKproof)$ and return $0$ if it fails. Else, compute
  $x,\tilde{s} \getr \ZZ^*_p, A \gets (\gen{g}_1\Ccom \gen{g}^{\tilde{s}}
  \prod_{i \in |\smsg|}\gen{h}_i^{\smsg_i})^{1/(\SBCMsk+x)}$. Send
  $(A,x,\tilde{s})$ to User.
\item \underline{User}: If $A = 1_{\GG_1}$: return $0$. Else, compute
  $s \gets r + \tilde{s}$. If $e(A,\gen{g}_2)^xe(A,\SBCMvk) \neq
  e(\gen{g}_1\Ccom\gen{g}^{\tilde{s}}\prod_{i \in |\smsg|}\gen{h}_i^{\smsg_i},
  \gen{g}_2)$: return $0$. Else, return $(A,x,s)$.
\end{itemize}

Note that, if needed, it is straightforward to augment the proof \NIZKproof
produced by the user in the first step with an extended proof that also proves
that $(x,w) \in \NIZKRel$, for some other relation \NIZKRel, thus implementing
the augmented interface $\langle\SBCMCom^\NIZKRel,\SBCMSign^\NIZKRel\rangle$ as
described earlier.

@@

\paragraph{Proving Knowledge of Signature.} %
Note that proving knowledge of a BBS+ signature as produced in our \SBCM variant
is essentially the same as in \cite{asm06,cdl16b}, only needing to account for
the different basis for messages signed in committed and plain form.

@@

\paragraph{OMF security.} The proof for OMF security is essentially the
same as that of EUF security for BBS+ signatures \cite{cdl16b}, which gives a
reduction against the $q$-SDH problem. There is only one exception: in the proof
for BBS+ EUF-security, when the adversary against EUF-security queries a
signature, the simulator (the adversary against $q$-SDH) has to simulate the
signature. For this, it requires the $l$ messages in the message set to be
signed, which in plain BBS+ it is not a problem, as they are received in the
clear. In the case of \SBCM, however, some of the messages to be signed are
received as part of a commitment. Note however that, in \SBCM, besides receiving
the commitment, we also receive a NIZK proof of knowledge of the corresponding
messages. Thus, the adversary against $q$-SDH in the OMF case only needs to
extract the witnesses from the proof. This is doable after soundness of NIZK.
If the NIZK also has online-extractability, then we do not need to impose
further requirements. If it is not, then the \SBCM scheme should not allow
parallel signing requests, or limit the total number of signatures to be
created to a logarithmic function of the security parameter (which is probably
not reasonable in most cases; although it may be for group signature-like
settings). We refer to \cite[Lemma 1]{cdl16b} for the full details of the proof
of EUF security in BBS+.
%
\jdv{If needed, do the actual proof. Should essentially be a copy-paste of
  that in \cite{cdl16b}...}

\paragraph{Blindness.} Blindness of \SBCM is a direct consequence of the
hiding property of the underlying block commitment scheme. Indeed, assume an
adversary $\adv$ against blindness of \SBCM. Then, $\adv$ can be used by
\advB against the hiding property of the commitment scheme in a straightforward
manner. That is, once $\adv$ outputs its two sets of messages to be signed in
committed form (i.e., $\overline{\smsg}_0$ and $\overline{\smsg}_1$, it feeds
them directly to its environment in \ExpComHideb; \advB awaits for the response
(a commitment of $\overline{\smsg}_b$), and forwards it to $\adv$. Finally,
\advB outputs whatever $\adv$ outputs. Clearly, if $\adv$ wins the blindness
game for \SBCM with non-negligible probability, so does \advB agains the hiding
game of the commitment scheme.

>>>>

\iffalse
\subsection{Digital Signatures}
\label{sapp:digital-signatures}

@@

\begin{figure}[ht!]
  \scalebox{0.9}{  
    \begin{minipage}[t]{\textwidth}
      \centering
      \procedure{$\ExpEUF(\Ssecpar)$}{%
        \Sparm \gets \SSetup(\Ssecpar) \\
        (\Svk,\Ssk) \gets \SKeyGen(\Sparm) \\
        (\Ssig,\msg) \gets \adv^{\SSign(\Ssk,\cdot)}(\Svk) \\
        \pcif \SVerify(\Svk,\Ssig,\msg) = 0: \pcreturn 0 \\
        \pcif \msg~\textrm{was not queried to \SSign}: \pcreturn 1 \\
        \pcreturn 0
      }
    \end{minipage}
  }
  \label{fig:euf-game}
  \caption{Existential Unforgeability Game.}
\end{figure}
\fi

@@

Although we don't expose commitments directly in our \UAS scheme or
constructions, they are an essential part of \SBCM schemes. Thus, we overview
them briefly next. In a nutshell, a commitment scheme is defined by the
following algorithms:

@@

To the best of our knowledge, models of existing schemes for signing blocks of
messages like \cite{cl02,asm06,ps16,cdl16b} target the case of signing blocks
of \emph{plain} messages, and are subsequently informally extended to support
signing commitments to blocks of messages via interactive protocols. However,
they do not support signing both committed and plain messages (although the
extension is trivial); and, more importantly, do not give security models of
the resulting construction, nor of course prove its security. While extending
the constructions seems straightforward, the modelling needs to be changed due
to the mentioned nuance of the conventional EUF notion not being compatible with
interactive signing protocols where the signer does not learn (some of) the
signed message(s). As we use this variant as a generic building block,
we briefly model such a scheme for Signatures over Blocks of Committed Messages
(\SBCM).

@@

\begin{description}
\item[$\SBCMparm \gets \SBCMSetup(\SBCMsecpar)$.] It produces public parameters
  for the other algorithms, given an input security parameter \SBCMsecpar.
\item[$(\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm)$.] Generates a
  verification-signing key pair.
\item[$(\SBCMcom,\pi,r) \gets \SBCMBlind(\SBCMvk,\osmsg,\smsg)$.] A user
  computes commitment \SBCMcom to request a signature over messages \osmsg (in
  committed form) and \smsg (in plain form), to signer with verification key
  \SBCMvk. The output is the commitment \SBCMcom, the randomness $r$ used to
  compute it, and a proof $\pi$ proving knowledge of \osmsg and \smsg in
  \SBCMcom.
\item[$\SBCMbsig \gets \SBCMSign(\SBCMsk,\SBCMcom,\pi,\smsg)$.] The
  signer, with signing key \SBCMsk, produces a blind signature \SBCMbsig over
  the messages commited to in commitment \SBCMcom, as well as the messages in
  \smsg, with associated proof $\pi$.
\item[$\SBCMsig \gets \SBCMUnblind(\SBCMvk,\SBCMbsig,\SBCMcom,r,\osmsg,\smsg)$.]
  A user, who requested a signature over \osmsg and \smsg, where \SBCMcom is a
  commitment over \osmsg using randomness $r$, finalizes the signature,
  computing \SBCMsig from the signer's partial signature \SBCMbsig.
\item[$1/0 \gets \SBCMVerify(\SBCMvk,\SBCMsig,\osmsg,\smsg)$.] Checks
  whether \SBCMsig is a valid signature over the set of messages \osmsg and
  \smsg, under verification key \SBCMvk.
\end{description}

The correctness and security properties are then defined as follows.

\paragraph{Correctness.} %
Informally, an \SBCM scheme is correct if signatures generated between an honest
party running \SBCMBlind, an honest signer running \SBCMSign fed with the output
of \SBCMBlind and matching \smsg and signing key pair, and the user finally
running \SBCMUnblind over the partial signature by the signer and leveraging
the same randomness as in \SBCMBlind, produces a signature over \osmsg and \smsg
that is accepted by \SBCMVerify.

@@

\paragraph{Blindness.} %
Finally, the signer must not learn the plaintext values of the messages that are
signed in committed form. Note that this is a weaker notion than the usual
blindness property of (partially) blind signature schemes, where it is
additionally required that the adversary cannot link a signature to the signing
process that produced it. Informally, we capture this basically as the blinding
notion of a commitment scheme -- and formally define it in \ExpSBCMBlindb in
\figref{fig:sbcm-games}.
%
Note that, in the definition, we explicitly do not give back to the adversary
\adv~any full signature (i.e., after running \SBCMUnblind) obtained from values
returned by \adv, as this will allow the adversary to trivially check what
messages (among the ones he chose) was signed. While this may seem a too weak
notion, it is good enough for our needs, as in our \UAS construction we never
share actual signatures, but zero-knowledge proofs of knowledge of such
signatures.

An \SBCM scheme is blind if, for all p.p.t.
adversaries $\adv$, $|\Pr[\ExpSBCMBlindo(\SBCMsecpar) = 1] -
\Pr[\ExpSBCMBlindz(\SBCMsecpar) = 1]|$ is a negligible function of the security
parameter.

\begin{figure}[ht!]
  \scalebox{0.85}{
    \begin{minipage}[t]{0.62\textwidth}
      \centering      
      \procedure[linenumbering]{$\ExpSBCMOMF(\secpar)$}{%
        \parm \gets \Setup(\secpar) \\
        (\vk,\sk) \gets \KeyGen(\parm) \\
        \lbrace(\sig_i,\overline{\smsg}_i, \smsg_i)\rbrace_{i\in[n]} \gets
        \adv^{\Sign(\sk,\cdot,\cdot,\cdot)}(\vk) \\
        \pcif \exists i \in [n]~\st~\Verify(\vk,\sig_i,\osmsg_i,\smsg_i) = 0: \\
        \pcind \pcreturn 0 \\
        \pcif \exists i \neq j \in [n]~\st \\
        \pcind \smsg_i = \smsg_j \land \osmsg_i = \osmsg_j: \pcreturn 0 \\
        \pcif \adv~\textrm{called}~\Sign(\sk,\cdot,\cdot,\cdot)~
        \textrm{more than $n$ times}: \\
        \pcind \pcreturn 0 \\
        \pcreturn 1
      }
      % \procedure[linenumbering]{$\ExpSBCMEUF(\secpar)$}{%
      %   \parm \gets \SBCMSetup(\secpar) \\
      %   (\vk,\sk) \gets \SBCMKeyGen(\parm) \\
      %   (\sig,\overline{\smsg}, \smsg) \gets
      %   \adv^{\langle \cdot, \SBCMSign(\sk,\cdot) \rangle}(\vk) \\
      %   \pcif \SBCMVerify(\vk,\sig,\overline{\smsg},\smsg) = 0: \\
      %   \pcind \pcreturn 0 \\
      %   \overline{\smsg'} \gets \Extract(\sig,\utrans) \\
      %   \pcind \textrm{where \utrans is the signing transcript for \sig} \\
      %   \pcreturn \smsg' \neq \smsg
      % }
    \end{minipage}
      % \vspace*{0.5em}
    \begin{minipage}[t]{0.43\textwidth}
      \procedure[linenumbering]{$\ExpSBCMBlindb(\secpar)$}{%
        \parm \gets \Setup(\secpar) \\
        (\vk,\sk) \gets \KeyGen(\parm) \\
        % (\osmsg_0,\osmsg_1) \getr M \pccomment{$M \coloneqq$ message space} \\
        % (\st,\smsg) \gets \adv(\vk,\sk) \\
        % \pcfor d \in \bin: \\
        % \pcind (\com_d,\pi_d,r_d) \gets \SBCMCom(\vk,\osmsg_d,\smsg) \\
        % \pcind (\st,\bsig_d) \gets \adv(\st,\sk,\com_d,\pi_d,\smsg) \\
        % \pcind \sig_d \gets \SBCMUnblind(\vk,\bsig_d,r_d,\osmsg_d,\smsg) \\
        % b^* \gets \adv(\st,\sig_b,\sig_{1-b}) \\       
        b^* \gets \adv^{BLIND(\cdot,\cdot,\cdot)}(\vk),~\textrm{where:} \\
        \pcind BLIND(\osmsg_0,\osmsg_1,\smsg): \\
        \pcind \pcind (\com,\pi,r) \gets \Blind(\vk,\osmsg_b,\smsg); \\
        \pcind \pcind \pcreturn (\com,\pi) \\
        \pcreturn b = b^*
      }
    \end{minipage}
  }
  \label{fig:sbcm-games}
  \caption{Games for \SBCM schemes.
  }
\end{figure}

\paragraph{Augmented NIZKs.} %
Constructions of \SBCM (e.g. \cite{asm06}), as well as the formalization we just
described, require that the user proves, in zero-knowledge (via a NIZK),
knowledge of the messages to be signed in committed
form -- and the blinding factor used to hide them. Note that, in such
constructions, it is easy to extend their NIZK so that, instead of simply
proving knowledge of the messages signed in committed form, the party running
\SBCMBlind proves, in zero knowledge, some arbitrary claim over the messages to
be signed (both those in committed or plaintext form). This can be done by
extending the initial NIZK into a more general one. 
%
It is direct that, if the base \SBCM scheme satisfies blindness, then extending
it with an arbitrary zero-knowledge NIZK proof over the signed messages, still
maintains blindness (the adversary cannot distinguish which committed message
set is signed, in the blindness game).
%
We use this extension in our \CUASGen construction. Note that, under this
extension, we may also need to provide extra information to the \SBCMBlind,
\SBCMSign and \SBCMUnblind algorithms, as part of the extended statement being
proven, and new witnesses (even though some may not be part of the messages to
be signed). To make this explicit, we use the following notation to denote
that we use a NIZK for relation $\NIZKRel$, with values $x'$ and $w'$ that are
part of the statement being proven, but are not contained within the actual
\smsg or \osmsg:

\begin{itemize}
\item $(\Ccom,\pi,r) \gets \SBCMBlind^\NIZKRel(\vk,\osmsg,\smsg;x',w')$. Like
  \SBCMBlind, but for relation \NIZKRel, which requires extra values $x'$ and
  $w'$ for its statement and witnesses, beyond what may be included in \smsg and
  \osmsg, respectively.
\item $\SBCMbsig \gets \SBCMSign^\NIZKRel(\sk,\Ccom,\pi,\smsg;x')$. Like
  \SBCMSign, but for relation \NIZKRel, which requires extra values $x'$
  for its statement, beyond what may be included in \smsg.
\item $\SBCMsig \gets \SBCMUnblind^\NIZKRel(\vk,\SBCMbsig,\Ccom,r,\osmsg,\smsg;
  x',w')$. Like \SBCMUnblind, but for relation \NIZKRel, which requires extra
  values $x'$ and $w'$ for its statement and witnesses, beyond what may be
  included in \smsg and \osmsg, respectively.
\end{itemize}

\paragraph{Proofs of knowledge of a \SBCM signature.} %
Finally, in addition, we require that the produced signatures must be compatible
with (efficient) NIZK proofs of knowledge of a signature.

@@

\paragraph{$(\Ccom,\pi,r) \gets \SBCMBlind(\SBCMvk,\osmsg,\smsg)$.} %
If $|\smsg |>\nattrs$ or $|\osmsg|>\tnattrs$,
abort. Else, fetch fresh randomness $r \getr \ZZ^*_p$, compute $\Ccom \gets
\gen{g}^r\prod_{i \in [|\overline{\smsg}|]}\gen{\th}_i^{\overline{\smsg}_i}$,
and $\NIZKproof \gets \NIZKProve(\NIZKcrs,(r,\overline{\smsg}),\Ccom)$.
Output $(\Ccom,\NIZKproof,r)$.

\paragraph{$\SBCMbsig \gets \SBCMSign(\SBCMsk,\Ccom,\NIZKproof,\smsg)$.} %
If $|\smsg|>\nattrs$, abort. Else, run $\NIZKVerify(\NIZKcrs,\Ccom,\NIZKproof)$
and return $0$ if it fails. Else, compute $x,\tilde{s} \getr \ZZ^*_p, A \gets
(\gen{g}_1\Ccom \gen{g}^{\tilde{s}} \prod_{i \in |\smsg|}
\gen{h}_i^{\smsg_i})^{1/(\SBCMsk+x)}$. Return $\SBCMbsig \gets (A,x,\tilde{s})$.

\paragraph{$\SBCMsig \gets \SBCMUnblind(\SBCMvk,\SBCMbsig,\Ccom,r,
  \osmsg,\smsg)$.} %
Parse \SBCMbsig as $(A,x,\tilde{s})$
If $A = 1_{\GG_1}$: return $0$. Else, compute $s \gets r + \tilde{s}$. If
$e(A,\gen{g}_2)^xe(A,\SBCMvk) \neq e(\gen{g}_1\Ccom\gen{g}^{\tilde{s}}
\prod_{i \in |\smsg|}\gen{h}_i^{\smsg_i},\gen{g}_2)$: return $0$. Else, return
$(A,x,s)$.

% \paragraph{$\SBCMsig/\bot \gets \langle \SBCMCom(\SBCMvk,\overline{\smsg},
%   \smsg), \SBCMSign(\SBCMsk,\smsg) \rangle$.} %

% \begin{itemize}
% \item \underline{User}: If $|\smsg|>\nattrs$ or $|\overline{\smsg}|>\tnattrs$,
%   abort. Else, fetch fresh randomness $r \getr \ZZ^*_p$, compute $\Ccom \gets
%   \gen{g}^r\prod_{i \in [|\overline{\smsg}|]}\gen{\th}_i^{\overline{\smsg}_i}$,
%   and $\NIZKproof \gets \NIZKProve(\NIZKcrs,(r,\overline{\smsg}),\Ccom)$.
%   Send $(\Ccom,\NIZKproof)$ to Issuer.
% \item \underline{Signer}: If $|\smsg|>\nattrs$, abort. Else, run $\NIZKVerify
%   (\NIZKcrs,\Ccom,\NIZKproof)$ and return $0$ if it fails. Else, compute
%   $x,\tilde{s} \getr \ZZ^*_p, A \gets (\gen{g}_1\Ccom \gen{g}^{\tilde{s}}
%   \prod_{i \in |\smsg|}\gen{h}_i^{\smsg_i})^{1/(\SBCMsk+x)}$. Send
%   $(A,x,\tilde{s})$ to User.
% \item \underline{User}: If $A = 1_{\GG_1}$: return $0$. Else, compute
%   $s \gets r + \tilde{s}$. If $e(A,\gen{g}_2)^xe(A,\SBCMvk) \neq
%   e(\gen{g}_1\Ccom\gen{g}^{\tilde{s}}\prod_{i \in |\smsg|}\gen{h}_i^{\smsg_i},
%   \gen{g}_2)$: return $0$. Else, return $(A,x,s)$.
% \end{itemize}

@@

\paragraph{Augmented NIZKs.} %
If needed, it is straightforward to augment the proof \NIZKproof used
in \SBCMBlind, \SBCMSign and \SBCMUnblind  with an extended proof that also
proves that $(x,w) \in \NIZKRel$, for some other relation \NIZKRel (where
$\osmsg$ is part of $w$), thus implementing the augmented interface described
earlier for \SBCM schemes.

\paragraph{Proving Knowledge of Signature.} %
Proving knowledge of a BBS+ signature as produced in our \SBCM variant
is essentially the same as in \cite{asm06,cdl16b}, only needing to account for
the different basis for messages signed in committed and plain form.

@@

\paragraph{OMF security.} The proof for OMF security is essentially the
same as that of EUF security for BBS+ signatures \cite{cdl16b}, which gives a
reduction against the $q$-SDH problem. There is only one exception: in the proof
for BBS+ EUF-security, when the adversary against EUF-security queries a
signature, the simulator (the adversary against $q$-SDH) has to simulate the
signature. For this, it requires the $l$ messages in the message set to be
signed, which in plain BBS+ it is not a problem, as they are received in the
clear. In the case of \SBCM, however, some of the messages to be signed are
received as part of a commitment. Note however that, in \SBCM, besides receiving
the commitment, we also receive a NIZK proof of knowledge of the corresponding
messages. Thus, the adversary against $q$-SDH in the OMF case only needs to
extract the witnesses from the proof. This is doable after soundness of the NIZK
and binding of the commitment scheme. %
If the NIZK also has online-extractability, then we do not need to impose
further requirements. If it is not, then the \SBCM scheme should not allow
parallel signing requests, or limit the total number of signatures to be
created to a logarithmic function of the security parameter (which is probably
not reasonable in most cases; although it may be for group signature-like
settings). We refer to \cite[Lemma 1]{cdl16b} for the full details of the proof
of EUF security in BBS+.
%
% \jesus{If needed, do the actual proof. Should essentially be a copy-paste of
%   that in \cite{cdl16b}...}

\paragraph{Blindness.}
Blindness of \SBCM is a direct consequence of the hiding property of the
underlying block commitment scheme. Indeed, assume an adversary $\adv$ against
blindness of \SBCM. Then, $\adv$ can be used by \advB against the hiding
property of the commitment scheme in a straightforward manner. Namely, \advB
sets up the environment for \adv by running the \KeyGen algorithm using the
\vk it receives. Then, for every query that \adv makes to its $BLIND$ oracle,
\advB checks that the length of \smsg is acceptable (i.e., less than the
maximum length allowed by \SBCM), and forwards the query to its own $COM$
oracle using $\osmsg_0$ and $\osmsg_1$. To the output \Ccom of $COM$, \advB
appends a simulated proof $\pi$, and forwards $(\Ccom,\pi)$ to \adv. Finally,
\advB outputs whatever \adv~outputs. The simulation is correct due to the
zero-knowledge property of the underlying NIZK. Thus, \advB wins whenever
\adv~does.

### 2022-10-01 prism-backend/research/gsac/app-related-extra.tex
Added back issuance unforgeability to fix issuance flaw. Updated rest of the paper. Proofs can be improved.

\begin{theorem}[Unforgeability-1 of \CUASMPS]
  If the base \CUASGen construction is unforgeable according to
  \defref{def:forge-uas}, then \CUASMPS satisfies unforgeability-1 as defined in
  \cite{ngsy22}.
\end{theorem}

\begin{proof}
  Given an adversary \adv~against unforgeability-1 of \CUASMPS, as defined in
  the MPS model, we build \advB that breaks unforgeability of the underyling
  \CUASGen, as defined for \UAS.

@@

\begin{theorem}[Unforgeability of \CUASRAC]
  If the base \CUASGen construction has unforgeability according to
  \defref{def:forge-uas}, and $F$ is one-way, then \CUASRAC is an
  unforgeable RAC scheme.
\end{theorem}

\begin{proof}
  Given \adv~against unforgeability of \CUASRAC as defined in
  \figref{fig:model-rac}, we build an adversary \advB against unforgeability of
  \CUASGen as defined in \defref{def:forge-uas}.

@@

\begin{theorem}[Unforgeability of \CUASAC]
  If the base \CUASGenInt construction is unforgeable according to (the
  interactive version of) \defref{def:forge-uas}, and non-frameabile according
  to (the interactive version of) \defref{def:frame-uas}, then \CUASAC is an
  unforgeable AC scheme.
\end{theorem}

@@

  From the previous, the same reasoning as in \thmref{thm:forge-cuasac} applies
  to an adversary \adv~winning at line 5 of $\Exp^{forge}_{\adv,dac}$. Next,
  suppose that, from \utrans obtained at line 6, $ExtractChain$ outputs a
  delegation chain that makes \adv~win at line 10. This means that an
  uncorrupted issuer at position $i-1$ of the chain did not own a credential
  containing $D'$, but the issuer at position $i$ does. Then, either of the
  following must happen:

  \begin{itemize}
  \item The credential of the issuer at position $i$ is a forgery, meaning that
    it is a valid signature by the issuer at position $i-1$, who did not produce
    it. This can be used to break signature non-frameability of \CUASGenInt.
  \item The credential of the issuer at position $i$ is not a forgery, meaning
    that it is a valid signature by the issuer at position $i-1$, who did
    produce it. But this contradicts the conditions required by $\fissue^{n,D}$,
    and therefore breaks unforgeability of \CUASGenInt.
  \end{itemize}
  %
  \qed
\end{proof}

>>>>

\begin{theorem}[Unforgeability-1 of \CUASMPS]
  If the base \CUASGen construction has signature unforgeability according to
  \defref{def:sign-forge-uas}, then \CUASMPS satisfies unforgeability-1 as
  defined in \cite{ngsy22}.
\end{theorem}

\begin{proof}
  Given an adversary \adv~against unforgeability-1 of \CUASMPS, as defined in
  the MPS model, we build \advB that breaks signature unforgeability of the
  underyling \CUASGen, as defined for \UAS.

@@

\begin{theorem}[Unforgeability of \CUASRAC]
  If the base \CUASGen construction has signature unforgeability according to
  \defref{def:sign-forge-uas}, and $F$ is one-way, then \CUASRAC is an
  unforgeable RAC scheme.
\end{theorem}

\begin{proof}
  Given \adv~against unforgeability of \CUASRAC as defined in
  \figref{fig:model-rac}, we build an adversary \advB against signature
  unforgeability of \CUASGen as defined in \defref{def:sign-forge-uas}.

@@

\begin{theorem}[Unforgeability of \CUASDAC]
  If the base \CUASGenInt construction has issuance unforgeability according to
  (the interactive version of) \defref{def:issue-forge-uas}, signature
  unforgeability according to (the interactive version of)
  \defref{def:sign-forge-uas}, and non-frameable according to (the interactive
  version of) \defref{def:frame-uas}, then \CUASDAC is an unforgeable DAC
  scheme.
\end{theorem}

@@

  From the previous, the same reasoning as in \thmref{thm:forge-cuasac} applies
  to an adversary \adv~winning at line 5 of $\Exp^{forge}_{\adv,dac}$. Next,
  suppose that from \utrans, $ExtractChain$ outputs at line 6 a
  delegation chain that makes \adv~win at line 9. This means that an
  uncorrupted issuer at position $i-1$ of the chain did not own a credential
  containing $D'$, but the issuer at position $i$ does. Then, either of the
  following must happen:

  \begin{itemize}
  \item The credential of the issuer at position $i$ is a forgery, meaning that
    it is a valid signature by the issuer at position $i-1$, who did not produce
    it. This can be used to break signature non-frameability of \CUASGenInt.
  \item The credential of the issuer at position $i$ is not a forgery, meaning
    that it is a valid signature by the issuer at position $i-1$, who did
    produce it. But this contradicts the conditions required by $\fissue^{n,D}$,
    and therefore breaks issuance unforgeability of \CUASGenInt.
  \end{itemize}
  %
  \qed
\end{proof}
